Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-21 docs/report/report.tex
Update

\section{Methodology}
The majority of effort in this project thus far can be separated into two individual but complementary pieces. First, a significant effort effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags. Secondly, using information from the estimated quadrotor state, a state machine and a set of PID controllers were developed that tracks and lands on a desired target.

@@

\subsubsection{AprilTag Inception}

To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending). This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag. Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture. An example of this procedure is highlighted in Figure \ref{fig:apriltagInception}.

@@

In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing. We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.

>>>>

\section{Methodology}
This project can be separated into two individual but complementary components. First, a significant effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags. Secondly, using information from the estimated quadrotor state, a state machine and a PID position controller were developed to track and lands on a desired target.

@@

\subsubsection{AprilTag Inception}
To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending). This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag. Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture. An example of this procedure is highlighted in Figure \ref{fig:apriltagInception}.

@@

To achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing. We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.
